
\begin{longtable}{|c|p{12cm}|}
\caption{Functional Requirements} \label{tab:func_req} \\
\hline
\textbf{Identifier} & \textbf{Description} \\
\hline
\endfirsthead
\hline
\textbf{Identifier} & \textbf{Description} \\
\hline
\endhead

FR-ViewProperties-01 & The system should display list/grid available Ellensburg rental properties. \\ \hline
FR-ViewProperties-02 & The system should display properties address for each listing. \\ \hline
FR-ViewProperties-03 & The system should display monthly rent for each property. \\ \hline
FR-ViewProperties-04 & The system should display properties room type (1 Bedroom). \\ \hline
FR-ViewProperties-05 & The system should display each property’s pet policy. \\ \hline
FR-ViewProperties-06 & The system should display each property’s lease type. \\ \hline
FR-ViewProperties-07 & The system should display each property manager’s numbers. \\ \hline
FR-ViewProperties-08 & The system should display each property’s distance from CWU campus. \\ \hline
FR-ViewProperties-09 & The system should display property detail photo on detail card. \\ \hline
FR-ViewProperties-10 & The system should display “No provided” for missing data field. \\ \hline
FR-Viewproperties-11 & The system should support the application responsive layout. \\ \hline
FR-Viewproperties-12 & The system should handle errors and inform the user \\ \hline
FR-Viewproperties-13 & The system should fetch all available properties from the API. \\ \hline
FR-CompareProperties-01 & The system should allow users to add properties to a comparison list. \\ \hline
FR-CompareProperties-02 & The system should allow users to remove properties from comparison list. \\ \hline
FR-CompareProperties-03 & The system should show “Compare now” action button when properties are selected. \\ \hline
FR-CompareProperties-04 & The system should display a compare badge showing the number of selected properties. \\ \hline
FR-CompareProperties-05 & The system should display a side-by-side comparison of the properties. \\ \hline
FR-ViewWalkingDistance-01 & The system should use CWU campus as default origin for distance calculation. \\ \hline
FR-ViewWalkingDistance-02 & The system should display estimated waking distance (in miles) for each property. \\ \hline
FR-ViewWalkingDistance-03 & The system should display estimated waking time (in minutes) for each property. \\ \hline
FR-ViewWalkingDistance-04 & The system should handle walking distance error and inform the user \\ \hline
FR-ViewWalkingDistance-05 & The system should fetch walking-distance data from the API or routing service. \\ \hline
FR-ViewTransporation-01 & Thes system should list the nearest public transit stop to each property and show the distance. \\ \hline
FR-ViewTransporation-02 & The system should show all available bus route numbers connecting the property to CWU campus. \\ \hline
FR-ViewTransporation-03 & The system should display estimates of public transit travel time to CWU campus. \\ \hline
FR-ViewTransporation-04 & System should notify the user when the transit data is unavailable. \\ \hline
FR-ViewTransporation-05 & The system should fetch transit information from the API or transit data source. \\ \hline
FR-ViewTransporation-06 & The system should handle transitrelated errors and inform the user. \\ \hline
FR-FilterProperties-01 & The system should provide filters for price range. \\ \hline
FR-FilterProperties-02 & The system should provide filters for bedroom numbers. \\ \hline
FR-FilterProperties-03 & The system should provide filters for pet policy. \\ \hline
FR-FilterProperties-04 & The system should provide filters for property type. \\ \hline
FR-FilterProperties-05 & The system should provide filters for lease term. \\ \hline
FR-FilterProperties-06 & The system should update the result list immediately upon filter change. \\ \hline
FR-FilterProperties-07 & The system should update the map pins immediately upon filter change. \\ \hline
FR-FilterProperties-08 & The system should provide “Clear filter” option. \\ \hline
FR-FilterProperties-09 & The system should provide individual filter reset control. \\ \hline
FR-FilterProperties-10 & The system should handle filter‑related errors and inform the user. \\ \hline
FR-InteractiveMap-01 & The system should fetch map-related property data from the API. \\ \hline
FR-InteractiveMap-02 & The system should display an interactive map of Ellensburg \\ \hline
FR-InteractiveMap-03 & The system should allow map zooming. \\ \hline
FR-InteractiveMap-04 & The system should display property pins on the map. \\ \hline
FR-InteractiveMap-05 & The system should handle map-related errors and inform the user. \\ \hline
FR-AIAssistance-01 & The system should allow users to type natural language queries. \\ \hline
FR-AIAssistance-02 & The system should translate natural language queries into filter or action. \\ \hline
FR-AIAssistance-03 & The system should support property comparison through chat. \\ \hline
FR-AIAssistance-04 & The system should answer questions regarding the properties. \\ \hline
FR-AIAssistance-05 & The system should provide non-legal education guidance with link to source. \\ \hline
FR-AIAssistance-06 & The system should use current filters and selected properties to personalize responses. \\ \hline
FR-AIAssistance-07 & The system should avoid giving legal or financial advice. \\ \hline
FR-AIAssistance-08 & The system should include disclaimers for AI-generated content. \\ \hline
FR-AIAssistance-09 & The system should avoid generating sensitive or personal information. \\ \hline
FR-AIAssistance-10 & The system should fetch AI-related property or context data from the API. \\ \hline
FR-AIAssistance-11 & The system should handle AI‑related errors and inform the user. \\ 
\hline
\end{longtable}
