
\subsection{Purpose}

The purpose of this Software Requirements Specification (SRS) is to provide a description of the features, behavior, and constraints of the HOSE Rental (Housing for Students in Ellensburg) Application project. This document serves as the blueprint for the HOSE (Housing for Students in Ellensburg) Rental team and the client, ensuring a shared understanding of the system’s design, APIs, functional requirements, and non‑functional expectations. It acts as a single reliable reference for all system requirements, and any changes to the application's scope or features must be reflected and updated within this document. 

\subsection{Scope of the Project}

\renewcommand{\arraystretch}{1.5}

\begin{longtable}{|>{\bfseries}p{4cm}|p{10cm}|}
\caption{Features In Scope} \label{tab:in_scope} \\
\hline
\multicolumn{2}{|c|}{\textbf{In Scope}} \\
\hline
\textbf{Feature} & \textbf{Description} \\
\hline
Interactive Map & Interactive map of Ellensburg showing all properties. \\
\hline
Walking Distance & Showing walking distance calculation from user-selected locations to each property or from the CWU campus. \\
\hline
Public Transit Information & Public transit information relevant to each property, such as routes, bus stops, and travel time. \\
\hline
Searchable Database & Containing available rental options in the Ellensburg area. \\
\hline
Property Details & 
\begin{tabular}[t]{@{}l@{}}
Lease agreement summary\\
Monthly rent\\
Number of rooms\\
Pet policy
\end{tabular} \\
\hline
Comparison Tool & Allowing users to compare properties by their prices, number of rooms, distance, etc. \\
\hline
AI Assistant (LLM-Based) & 
\begin{tabular}[t]{@{}l@{}}
Summarizing user reviews\\
Answering user queries\\
Provide rental history
\end{tabular} \\
\hline
\end{longtable}

\vspace{1cm}

\begin{longtable}{|>{\bfseries}p{4cm}|p{10cm}|}
\caption{Not In Scope} \label{tab:not_in_scope} \\
\hline
\multicolumn{2}{|c|}{\textbf{Not in Scope}} \\
\hline
\textbf{Feature} & \textbf{Description} \\
\hline
Payment Processing & The application and backend services must remain free. \\
\hline
Real-time Rental Availability Update & The application will not provide real-time availability updates from landlords or property management systems. \\
\hline
Landlord/Property Management Dashboard & Unique views or management tabs for the Ellensburg properties. \\
\hline
User/Admin Accounts & Because HOSE is not storing emails or passwords, there will be no need for account creation. \\
\hline
\end{longtable}

\subsection{Glossary}

\renewcommand{\arraystretch}{1.5} 

\rowcolors{2}{gray!10}{white}

\begin{table}[H]
\centering
\caption{Glossary of Terms}

\begin{tabularx}{\textwidth}{>{\bfseries}lX}
\toprule
\rowcolor{gray!30}
Term & Definition \\
\midrule
API & Set of protocols that allow different software systems to communicate and interact with each other. \\
Test & Ensures the functionality of an API or service, verifying that it behaves as expected. \\
Prototype & An early functional model of a product or feature, used to visualize and test concepts before full development. \\
Payload & Data being sent or received by the API, often containing information relevant to a request or response. \\
\bottomrule
\end{tabularx}
\end{table}


\subsection{References}


\renewcommand{\arraystretch}{1.5}
\rowcolors{2}{gray!10}{white}

\begin{table}[H]
\centering
\caption{References}

\begin{tabularx}{\textwidth}{>{\bfseries}lX>{\raggedright\arraybackslash}X}
\toprule
\rowcolor{gray!30}
Name & Source (Link) & Description \\
\midrule
Google Maps & \href{https://www.google.com/maps}{Google Maps} & We use it as a reference for UI design, interactive maps, and navigation features. \\
LLM with Geospace & \href{https://doi.org/10.3390/ijgi13100348}{https://doi.org/10.3390/ijgi13100348} & Refer to how an AI assistant can be integrated and how it has already been applied in geospatial systems. \\
\bottomrule
\end{tabularx}
\end{table}