

\begin{longtable}{|c|p{12cm}|}
\caption{Non-Functional Requirements} \label{tab:none_func_req} \\

\hline
\textbf{Identifier} & \textbf{Description} \\
\hline
\endfirsthead
\hline
\textbf{Identifier} & \textbf{Description} \\
\hline
\endhead



NFR-ViewProperties-01 & The property list should be loaded within 2 seconds under normal network conditions. \\ \hline
NFR-ViewProperties-02 & Property photos and details should be rendered without noticeable layout shifts. \\ \hline
NFR-ViewProperties-03 & The system should display property detail apply/schedule tour link \\ \hline
NFR-ViewProperties-04 & The system should handle up to 5000 property records without performance degradation. \\ \hline
NFR-ViewProperties-05 & The system should display error messages for property loading within 1 second or detection. \\ \hline
NFR-ViewProperties-06 & The system should display review. \\ \hline
NFR-ViewProperties-06 & The system should allow users to save/ unsaved properties. \\ \hline
NFR-CompareProperties-01 & The system should visually highlight differing values between properties. \\ \hline
NFR-CompareProperties-02 & The system should allow users to export the comparison list as pdf. \\ \hline
NFR-CompareProperties-03 & The system should allow users to save a named comparison set. \\ \hline
NFR-CompareProperties-04 & The comparison table should display within 1 second after selecting “Compare now.” \\ \hline
NFR-ViewDistance-01 & The system should allow users to change origin by typing the address. \\ \hline
NFR-ViewDistance-02 & The system should allow users to change origin by pinned map point. \\ \hline
NFR-ViewDistance-03 & The system should have “view route” button. \\ \hline
NFR-ViewTransporation-01 & The system should display Walking distance to the nearest transit stop. \\ \hline
NFR-ViewTransporation-02 & The system should display transfer information. \\ \hline
NFR-ViewTransporation-03 & The system should predict real-time live delay. \\ \hline
NFR-ViewTransporation-04 & The system should provide transit lines and stop in map. \\ \hline
NFR-FilterProperties-01 & The system should be provided “sort by”. \\ \hline
NFR-FilterProperties-02 & Filter operations should not require page reloads and must update smoothly. \\ \hline
NFR-FilterProperties-03 & If filters fail to apply, the fallback list should display within 1 second. \\ \hline
NFR-InteractiveMap-01 & The map must load and become interactive within 1 seconds. \\ \hline
NFR-InteractiveMap-02 & Map panning and zooming must maintain at least 30 FPS. \\ \hline
NFR-InteractiveMap-03 & The system shall not support streetlevel satellite imagery. \\ \hline
NFR-InteractiveMap-04 & The system shall not support streetlevel 3D map view. \\ \hline
NFR-InteractiveMap-05 & If map data fails to load, a fallback “Unable to load map” message must appear within 1 second. \\ \hline
NFR-AIAssistance-01 & The system AI responses should generate within 2 seconds for typical queries \\

\hline 
\end{longtable}

