\documentclass{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{array}
\usepackage{booktabs}
\usepackage{float}
\usepackage{caption}
\usepackage{parskip}


\title{SRS Capstone Group 2}

\author{Alex Buckley}
\author{Jeremy Gutierrez}
\author{Cole Manchester}
\author{Aty Sokoy}
\author{Yonatan Yemiru}

\affil{Central Washington University}
\date{January 2026}

\begin{document}

\maketitle

\section*{Document Information}
\addcontentsline{toc}{section}{Document Information}

\begin{table}[h]
\centering
\begin{tabular}{>{\bfseries}l l}
\toprule
Document Owner     & Rental Project \\
Issue Date         & January 9, 2026 \\
Last Saved Date    & --- \\
File Name          & Software Requirements Specification \\
\bottomrule
\end{tabular}
\end{table}

\section*{Document History}
\addcontentsline{toc}{section}{Document History}

\begin{table}[h]
\centering
\begin{tabular}{lll}
\toprule
Version & Issue Date & Changes \\
\midrule
1.0 & Jan 9, 2026 & SRS created \\
1.1 & Jan 9, 2026 & Introduction (Purpose, scope) \\
1.2 & Jan 15, 2026 & All actors and features identified \\
1.3 & Jan 21, 2026 & Revised scope and implemented use cases \\
\bottomrule
\end{tabular}
\end{table}

\newpage
\tableofcontents

\newpage
\section{Introduction}

\subsection{Purpose}

\subsection{Scope of the Project}

\subsection{Glossary}

\subsection{References}

\newpage
\section{Use Case Diagram}

\newpage
\section{Use Case Descriptions}

\subsection{Use case 1 - View Properties}
\subsubsection{Description}

\textbf{Use Case ID:} ViewProperties-01

\textbf{Priority:} High

\textbf{Source:} Functional Requirements

\textbf{Primary Actor:} User

\textbf{Secondary Actors:} N/A

\textbf{Description:} Allows users to view properties within the Ellensburg area. Each property includes data and filter options.

\textbf{Preconditions:} User can access the HOSE landing page.

\textbf{Trigger:} User is viewing the interactive map.

\textbf{Main Flow:}
\begin{itemize}
    \item User is on the HOSE landing page.
    \item User clicks the interactive map feature.
    \item The system displays current known properties available.
\end{itemize}

\textbf{Alternative Flows:}
\begin{itemize}
    \item User selects a specific property to view detailed apartment or home information.
    \item User exits without viewing any property details.
\end{itemize}

\textbf{Postconditions:} Properties are displayed to the user.

\textbf{Conclusion:} Users can view properties and contextual information about those properties within Ellensburg.

\textbf{Business Rules:} The system must respond within 5 seconds.

\textbf{Implementation Constraints:} Property data shall be stored using SQLite. HOSE accesses the database for each requested location to display relevant property data.

\textbf{Assumptions:} All location data is up to date for the year 2026.




\subsection{Use case 2 - Compare Properties}
\subsubsection{Description}

\textbf{Use Case ID:} CompareProperties-01

\textbf{Priority:} High

\textbf{Source:} Functional Requirements

\textbf{Primary Actor:} User

\textbf{Secondary Actors:} AI Chatbot

\textbf{Description:} Allows users to compare property details within the Ellensburg area. Selected properties are displayed side-by-side with highlighted data points for comparison.

\textbf{Preconditions:} User can access the HOSE landing page and has one property already selected.

\textbf{Trigger:} User selects a new property location to compare with the currently selected property.

\textbf{Main Flow:}
\begin{itemize}
    \item User selects a new property location on the map.
    \item The system displays data for both the originally selected property and the newly selected property.
    \item The system highlights the data points being compared on the map.
\end{itemize}

\textbf{Alternative Flows:}
\begin{itemize}
    \item User selects a property to view its data; the system displays the selected property information.
    \item User selects a second property to compare; the system displays the second property data adjacent to the original property.
    \item User selects a third property; the system deselects the original property and compares the second and third selected properties.
\end{itemize}

\textbf{Postconditions:} A new comparison property is selected and displayed.

\textbf{Conclusion:} Users can compare details between properties located in Ellensburg.

\textbf{Business Rules:} All location data must be loaded within 5 seconds.

\textbf{Implementation Constraints:} The system allows comparison of a maximum of two properties at a time.

\textbf{Assumptions:} Users will compare different locations and are willing to wait for data to load.




\subsection{Use case 3 - View Walking Distance}
\subsubsection{Description}




\textbf{Use Case ID:} ViewDistance-01

\textbf{Priority:} High

\textbf{Source:} Functional Requirements

\textbf{Primary Actor:} User

\textbf{Secondary Actors:} Walking Service

\textbf{Description:} Allows users to view properties within the Ellensburg area. Each property includes data, filter options, and walking distance information to CWU and nearby public transport access locations.

\textbf{Preconditions:} Users can access the Rental Assistant Tool landing page.

\textbf{Trigger:} User selects an individual property page to view detailed property info.

\textbf{Main Flow:}
\begin{itemize}
    \item User selects a property to view detailed info.
    \item The system queries the database for the selected property’s data.
    \item The system displays walking distance and time from the property to CWU and nearby public transport access locations.
\end{itemize}

\textbf{Alternative Flows:}
\begin{itemize}
    \item \textbf{Property data missing or corrupted:}
        \begin{itemize}
            \item User selects property to view detailed info.
            \item System queries database for selected property data.
            \item System does not find valid property data.
            \item System displays "Property not found" error.
        \end{itemize}
    \item \textbf{Walking data missing from property:}
        \begin{itemize}
            \item User selects property to view detailed info.
            \item System queries database for selected property data.
            \item System finds property data with walking data missing.
            \item System displays property without walking data.
        \end{itemize}
    \item \textbf{Site admin uploads new property successfully:}
        \begin{itemize}
            \item Site admin uploads new property.
            \item System validates property data.
            \item System queries Walking Service for walking data to CWU and bus stop locations.
            \item Walking Service responds with walking distance and time.
            \item System saves walking data with property.
            \item System informs site admin of successful upload.
        \end{itemize}
    \item \textbf{Walking service fails during property upload:}
        \begin{itemize}
            \item Site admin uploads new property.
            \item System validates property data.
            \item System attempts to query Walking Service a set number of times.
            \item Walking Service fails to respond successfully.
            \item System saves property with walking data missing.
            \item System informs site admin of upload walking data failure and property success.
            \item System runs scheduled CRON jobs to query Walking Service for properties with walking data missing.
        \end{itemize}
\end{itemize}

\textbf{Postconditions:} Property data has been retrieved and displayed (or error shown). No property data is modified.

\textbf{Conclusion:} User has viewed walking time and distance from the selected property to CWU and nearby bus stops.

\textbf{Business Rules:} Only properties within Ellensburg, applicable to CWU students, will be displayed. Walking distance is calculated using pedestrian-friendly routes only.

\textbf{Implementation Constraints:} Walking distance and time must be retrieved from the Walking Service API. Property data must be retrieved from the system’s property database.

\textbf{Assumptions:} Users have a stable internet connection and a device suitable for running client software. The Walking Service will eventually work if an error is encountered.




\subsection{Use case 4 - View Public Transportation}
\subsubsection{Description}

\textbf{Use Case ID:} ViewTransportation-01

\textbf{Priority:} High

\textbf{Source:} Functional Requirements

\textbf{Primary Actor:} User

\textbf{Secondary Actors:} Public Transit Service

\textbf{Description:} Allows users to view public transit options in the nearby area for each property location.

\textbf{Preconditions:} Users can access the HOSE landing page.

\textbf{Trigger:} User initiates viewing public transportation data.

\textbf{Main Flow:}
\begin{itemize}
    \item User clicks on public transportation data.
    \item User selects two destinations to travel between.
    \item HOSE performs a call to Google Maps Transit API with travelMode=Transit.
    \item System receives the transit schedule and map display.
    \item System displays the map with the transit path.
\end{itemize}

\textbf{Alternative Flows:}
\begin{itemize}
    \item \textbf{User edits travel preference:}
        \begin{itemize}
            \item User edits travel preference to walking instead of transit.
            \item HOSE automatically updates the map display and travel path with the appropriate method of travel.
        \end{itemize}
\end{itemize}

\textbf{Postconditions:} The user has an understanding of how far they are from transit, home, school, and other locations.

\textbf{Conclusion:} The user has transportation data to help them choose the right apartment.

\textbf{Business Rules:} Users have reliable transportation to multiple destinations.

\textbf{Implementation Constraints:} Users will see the closest transit center to the selected apartment first.

\textbf{Assumptions:} Users will search for one transit center at a time per apartment.






\subsection{Use case 5 - Filter Properties}
\subsubsection{Description}

\textbf{Use Case ID:} ViewProperties1

\textbf{Priority:} High

\textbf{Source:} Functional Requirements

\textbf{Primary Actor:} User

\textbf{Secondary Actors:} N/A

\textbf{Description:} Allows users to view and filter properties within the Ellensburg area. Each property includes data and multiple filter options.

\textbf{Preconditions:} User can access the Rental Assistant Tool landing page.

\textbf{Trigger:} User selects at least one filter option on the filter modal while using the interactive map.

\textbf{Main Flow:}
\begin{itemize}
    \item User navigates to the interactive map.
    \item System retrieves viewable properties from the database.
    \item System displays properties on the interactive map.
    \item User selects one or more fields to filter from the filter modal.
    \item System filters properties by all selected fields.
    \item System displays only filtered properties on the interactive map.
\end{itemize}

\textbf{Alternative Flows:}
\begin{itemize}
    \item \textbf{User resets filter options:}
        \begin{itemize}
            \item User is viewing the map with one or more filters applied.
            \item User selects "remove all filters" from the filter modal.
            \item System displays all properties within the current viewport.
        \end{itemize}
    \item \textbf{User updates or modifies filters:}
        \begin{itemize}
            \item User removes, adjusts values, or adds new filters in the filter modal.
            \item System filters all properties by the user-selected filters.
            \item System displays the updated collection of filtered properties.
        \end{itemize}
    \item \textbf{No properties match all filter requirements:}
        \begin{itemize}
            \item User selects filters from the filter modal.
            \item System filters properties by all selected fields.
            \item No properties pass all filter criteria.
            \item System displays the interactive map with no properties.
            \item System informs the user that no properties match the selected filters.
        \end{itemize}
\end{itemize}

\textbf{Postconditions:} Property data has been retrieved and displayed on the interactive map. Filtered-out properties will not be displayed. No property data is modified.

\textbf{Conclusion:} User sees all properties passing filter criteria within the viewport on the interactive map. If no property meets the criteria, the user is informed.

\textbf{Business Rules:} Only properties within Ellensburg, applicable to CWU students, will be displayed. Filterable fields include, but are not limited to, minimum rent price, maximum rent price, lease type, pets allowed, walking distance to CWU, and walking distance to the nearest bus stop.

\textbf{Implementation Constraints:} Property data must be retrieved from the system’s property database. Properties must be displayed at the correct location on the interactive map.

\textbf{Assumptions:} Users have a stable internet connection and a device suitable for running client software.





\subsection{Use case 6 - View Interactive Map}
\subsubsection{Description}

\textbf{Use Case ID:} ViewProperties1

\textbf{Priority:} High

\textbf{Source:} Functional Requirements

\textbf{Primary Actor:} User

\textbf{Secondary Actors:} Mapping Service

\textbf{Description:} Allows users to view properties and other relevant locations on an interactive map within the Ellensburg area. Each property includes data and filter options, and map locations such as bus stops are overlaid dynamically.

\textbf{Preconditions:} User can access the Rental Assistant Tool landing page.

\textbf{Trigger:} User navigates to the interactive map page.

\textbf{Main Flow:}
\begin{itemize}
    \item User navigates to the interactive map page.
    \item System queries the database for locations, including properties and bus stops.
    \item System requests map area from the Map Service.
    \item Map Service responds with map data.
    \item System displays received map data.
    \item System overlays locations from the database on the map.
    \item User pans or scrolls the interactive map.
    \item System hides and displays locations as they come in and out of the viewport.
    \item System requests additional map data from Map Service if viewport bounds exceed the loaded area.
    \item Map Service responds with additional map data.
    \item System displays new map data and overlays locations from the database.
    \item User clicks a property on the interactive map.
    \item System queries the property database for detailed property data.
    \item System displays detailed data of the selected property.
\end{itemize}

\textbf{Alternative Flows:}
\begin{itemize}
    \item \textbf{User pans to an area with no properties:}
        \begin{itemize}
            \item User pans outside of Ellensburg.
            \item System queries the property database for locations.
            \item System displays no locations, as none exist within the viewport.
        \end{itemize}
    \item \textbf{Map Service fails to respond with valid data:}
        \begin{itemize}
            \item User loads or pans the map.
            \item System queries the database for locations and requests map data from the Map Service.
            \item Map Service fails to respond after a set number of retries.
            \item System informs the user that the map failed to load.
            \item System displays properties as a list, still allowing access to individual property detail pages.
            \item System intermittently retries requests to the Map Service.
        \end{itemize}
\end{itemize}

\textbf{Postconditions:} User has sufficient data to compare multiple properties on the interactive map.

\textbf{Conclusion:} Users can explore and select properties from the interactive map to view detailed information.

\textbf{Business Rules:} Only properties within Ellensburg, applicable to CWU students, will be displayed. Bus stops within Ellensburg will also be displayed.

\textbf{Implementation Constraints:} Location data must be received from the system’s database. Map data must be received from the Map Service. Locations must be displayed at the correct coordinates.

\textbf{Assumptions:} Users have a stable internet connection and a device suitable for running client software. The Map Service will eventually respond if an error is encountered.





\subsection{Use case 7 - AI Assistant Interactions}
\subsubsection{Description}

\newpage
\section{Functional Requirements}

\newpage
\section{Non-Functional Requirements}

\newpage
\section{API interfaces}

\newpage
\section{LLM Model}



\end{document}
